|

### 2019-09-06 inst/manuscript/candidaev_figures.Rmd
Track compressed manuscript figure .tiff files
Manuscript figure .tiff files with lzw compression are
a more manageable size, therefore track with git.

# arguments for figure 1 export
f1_args <- list(tiff = list(type = "cairo"))
```

@@

# arguments for figure 2 export
f2_args <- list(tiff = list(type = "cairo"))
```

@@

# arguments for figure 3 export
f3_args <- list(tiff = list(type = "cairo"))
```

@@

# arguments for figure 4 export
f4_args <- list(tiff = list(type = "cairo"))
```

@@

# arguments for figure 5 export
f5_args <- list(tiff = list(type = "cairo"))
```

@@

# arguments for figure 6 export
f6_args <- list(tiff = list(type = "cairo"))
```

@@

# arguments for figure 7 export
f7_args <- list(tiff = list(type = "cairo"))
```

@@

# arguments for figure 8 export
f8_args <- list(tiff = list(type = "cairo"))
```

>>>>

# arguments for figure 1 export
f1_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

@@

# arguments for figure 2 export
f2_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

@@

# arguments for figure 3 export
f3_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

@@

# arguments for figure 4 export
f4_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

@@

# arguments for figure 5 export
f5_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

@@

# arguments for figure 6 export
f6_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

@@

# arguments for figure 7 export
f7_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

@@

# arguments for figure 8 export
f8_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```
